Crystal as a thermodynamic computer

### 2024-09-16 paper/main.tex
update main figure, add description for eqa (8).

    \end{tikzpicture}
    \caption{A surface programmable thermodynamic computer (TC) that implements the rule 110 elementary cellular automata. The vertical direction is the space axis,
    while the horizontal direction is the time axis.
    The computation is done by moving the heat zone (orange colored area) from the input surface (left) to the output surface (right) slowly with a constant speed $v$.
    The TC has a translational invariant structure, and each unit cell (inset) is a $110$ rule cellular automata gadget that consists of 5 mutually correlated spins (white circles).
    % \jinguo{please add symbols for space, time and width}
    \ym{I add symbols. please check if i still need to put original captions here}
    \jinguo{please make the circles and texts in the inset larger}
    }

@@

We can define an effective heat zone with width $W'$ as the width of the raising edge of the temperature distribution, where the spins can be cooled actively.
%Defining $\Delta E_{max}$ to be the largest possible energy change when a spin is fliped.
%The effective heat zone with width $W'(\Lambda)$ should then be $[y-W'(\Lambda), y]$, where position $y$ satisfying 
%$\exp(\frac{\Delta E_{max}}{T(y)}) = 0.1$ and $y<L(t)$. 
% Since the layers in fronts of the effective heat zone can only be fliped with a $\epsilon$ probability if the local energy would increase. 
The spins outside the effective heat zone are either frozen (too cold) or flip randomly (too hot).
As a spin flips with a probability $\sim e^{-\Delta E/T}$, the cold edge of the heat zone can be defined as the position where the probability of flipping is $\epsilon$.
We have $W'$ scales with the required error probability $\epsilon$ as:
\begin{equation}
    e^{-\frac{\Delta E}{T_{\rm max}}\Lambda^{cW'}} \sim \epsilon
\end{equation}
where $c$ is an empirical constant and can be determined during the experiment. 
\ym{I am not sure about how to give a concrete definition of the effective width $W'$.}\jinguo{How about this?}
We have $\log(\Lambda) cW' \sim \log(\frac{T_{\rm max}}{\Delta E}\log(\frac{1}{\epsilon}))$.

Combining with \Cref{eq:totaltime}, the total annealing time can be estimated as
\begin{equation}
    \label{eq:total-annealing-time}
    t_{\rm total} \sim \frac{M}{W'}\left(\ln\left(\frac{M}{W'}\right)\right)^{1+ \frac{1}{c\ln(\Lambda)}}
\end{equation}

@@

\begin{figure*}[]
    \centering
    \vspace*{-\topskip}
    \includegraphics[width=\textwidth,keepaspectratio]{../notes/images/main_result.pdf}
    \caption{Numerical Result.
    \jinguo{images should use the pdf format, the font size should be larger. Is it possible to verify that the Ising model is similar to the toy model? What is $T$ in the xlabel?}
    \ym{If a comparison between Ising model and toy model is a must, plese inform me.}
    \jinguo{(1) We should make the lines in (c) fit better with the data points. (2) Please complete the caption. You need to at least explain the short notations: GA, HB. (3) Please use log-scale axes for (a) and (c), instead of taking log directly on the data points. $\ln(\ln(M))$ is difficult to interpret.}
    }
    \label{fig:main-numerical-result}
\end{figure*}

@@

\section{Physical implementation on Ising machine}\label{spin-glass}

>>>>

    \end{tikzpicture}
    \caption{A surface programmable thermodynamic computer (TC) that implements the rule 110 elementary cellular automata. The vertical direction is the space axis,
    while the horizontal direction is the time axis.
    The computation is done by moving the heat zone (orange colored area) from the input surface (left) to the output surface (right) slowly with a constant speed $v$.
    The TC has a translational invariant structure, and each unit cell (inset) is a $110$ rule cellular automata gadget that consists of 5 mutually correlated spins (white circles).
    % \jinguo{please add symbols for space, time and width}
    % \ym{I add symbols. please check if i still need to put original captions here}
    \jinguo{please make the circles and texts in the inset larger}
    }

@@

We can define an effective heat zone with width $W'$ as the width of the raising edge of the temperature distribution, where the spins can be cooled actively.
%Defining $\Delta E_{max}$ to be the largest possible energy change when a spin is fliped.
%The effective heat zone with width $W'(\Lambda)$ should then be $[y-W'(\Lambda), y]$, where position $y$ satisfying 
%$\exp(\frac{\Delta E_{max}}{T(y)}) = 0.1$ and $y<L(t)$. 
% Since the layers in fronts of the effective heat zone can only be fliped with a $\epsilon$ probability if the local energy would increase. 
The spins outside the effective heat zone are either frozen (too cold) or flip randomly (too hot).
As a spin flips with a probability $\sim e^{-\Delta E/T}$, the cold edge of the heat zone can be defined as the position where the probability of flipping is $\epsilon$.
We have $W'$ scales with the required error probability $\epsilon$ as:
\begin{equation}
    e^{-\frac{\Delta E}{T_{\rm max}}\Lambda^{cW'}} \sim \epsilon
\end{equation}
where $c$ is an empirical constant and can be determined during the experiment. 
\jinguo{How about this?}
\ym{But I still don't think the constant $c$ is reasonable in this version. Anyway it is a better 
description for $W'$.}

We can further derive $e^{W'}$ as function of $\Lambda$:
\begin{equation}
    e^{\ln(\Lambda)cW'}\sim \ln(\frac{1}{\epsilon})\rightarrow e^{W'}\sim \ln(\frac{1}{\epsilon})^{\frac{1}{c\ln(\Lambda)}}
\end{equation}

Combining with \Cref{eq:totaltime} and $\epsilon \sim \frac{W'}{M}$, the total annealing time can be estimated as
\begin{equation}
    \label{eq:total-annealing-time}
    t_{\rm total} \sim \frac{M}{W'}\left(\ln\left(\frac{M}{W'}\right)\right)^{1+ \frac{1}{c\ln(\Lambda)}}
\end{equation}

@@

\begin{figure*}[]
    \centering
    \vspace*{-\topskip}
    \includegraphics[width=\textwidth,keepaspectratio]{../notes/images/main_result.pdf}
    \caption{Numerical Result. (a) The moving speed $v$ of the heat bath is proportional
    to $\ln(M)^{f(\Lambda)}$, where the power function $f(\Lambda)$ can be determined
    by fitting the slope. (b) The total annealing time $T_c$ scales linearly with the
    number of spins in single layer $N$. (c) The total annealing time $T_c$ with different annealing methods,
    including heat bath (HB) moving forward, heat bath (HB) moving backward, Global annealing (GA) with input spins fixed and
    Global annealing (GA) with output spins fixed. The latter three methods are all hard to cool the system.
    \jinguo{images should use the pdf format, the font size should be larger. Is it possible to verify that the Ising model is similar to the toy model? What is $T$ in the xlabel?}
    \ym{If a comparison between Ising model and toy model is a must, plese inform me.}
    \jinguo{(1) We should make the lines in (c) fit better with the data points. (2) Please complete the caption. You need to at least explain the short notations: GA, HB. (3) Please use log-scale axes for (a) and (c), instead of taking log directly on the data points. $\ln(\ln(M))$ is difficult to interpret.}}
    \label{fig:main-numerical-result}
\end{figure*}

@@

% \section{Physical implementation on Ising machine}\label{spin-glass}
